Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible. Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns. Developers can run the tool to analyze the side-channels leakages and fix these patterns. However, fixing all
those leakages seem not feasible in practice.  Tremendous efforts havebeen made to remove the side-channel vulnerabilities in cryptography
libraries in the past decade. However,  there are
several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
have better performance, such as the T-table lookups in AES, CRT
optimizations in RSA, and Fast Fourier Transform (FFT) in many media
processing libraries. For many non-cryptography developers, side
channels are not in consideration usually. However, recent
studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.

The key to solving the problem is looking for a proper metric to assess the side-channel leakages' sensitive level. Many side-channel analysis tools focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries. For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the encryption algorithm's strength. However, many attacks also exploit non-cryptography libraries and applications like machine learning applications~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on cryptography libraries that exploit one vulnerability at a time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information. Suppose one program has two leakage sites. It is hard to estimate the total effect of two leakages. Any two leakages have some underlying complex relationships. That is, the two leakages could be completely independent, which means they leak different information. Alternatively, the two leakages could leak the same information. A typical situation, that is, the two leakage sites, can leak some common knowledge. Apart from that, they have their unique leakages. However, no existing tools that can estimate the total effect of multiple leakage sites. For real-world applications with thousands of lines, it is hard to estimate the amount of leaked information. Attackers can guess the values of some temporary values. But temporary values contain some knowledge of the original secret buffer.

Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. It is hard to implement these techniques from scratch. So they build the tool on top of existing binary analysis frameworks. Due to the limitations of existing binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries. For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools can not handle it. Moreover, some binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited in analyzing floating-point instructions. But the functionality of these applications heavily depends on floating-point calculations.

Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of these vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}. There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage. These tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But these tools can not tell software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.

>>>>

While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible. Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns. Developers can run the tool to analyze the side-channels leakages and fix these patterns. However, fixing all
those leakages seem not feasible in practice.  Tremendous efforts havebeen made to remove the side-channel vulnerabilities in cryptography
libraries in the past decade. However,  there are
several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
have better performance, such as the T-table lookups in AES, CRT
optimizations in RSA, and Fast Fourier Transform (FFT) in many media processing libraries. For many non-cryptography developers, side-channels are not in consideration usually. However, recent studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.

Even a minor leakage can be severe for cryptography libraries because
the leakage can reduce the encryption algorithm's strength. However,
many attacks also exploit non-cryptography libraries and applications
like machine learning
applications~\cite{yan2020cache,hong2018security}, graphic
libraries~\cite{wang2019unveiling}, spell checking
tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
cryptography libraries that exploit one vulnerability at a time,
attacks on non-cryptography rely on multiple side-channel leakage
sites to retrieve more information. Suppose one program has two
leakage sites. It is hard to estimate the total effect of those two
leakages. However, no existing tools that can estimate the total
effect of multiple leakage sites. For real-world applications with
thousands of lines, it is hard to estimate the amount of leaked
information. Attackers can guess the values of some temporary
values. And those temporary values contain some knowledge of the
original secret buffer.

Second, many side-channel leakage detection tools rely on
techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
to the limitations of existing binary analysis techniques, it is hard to apply existing methods to analyze side-channels in non-cryptography
libraries. For many other applications like machine learning, media,
and graphic libraries built on the top architecture-dependent
libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools are not able to
handle them. Moreover, some binary analysis frameworks (e.g.,
Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
floating-point instructions. However, the functionality of those
applications heavily depends on floating-point calculations.

Third, while many existing works can detect side-channel leakages, few
of them can assess the severity levels of those
vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
Some existing tools~\cite{182946,chattopadhyay2019quantifying, biondi2018scalable,5207642,pasareanu2016multi,AskarovC12,phan2017synthesis} quantify the information leakage by giving an upper
bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
those tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.  Often the over-approximated estimate is very far away from the amount of real leakage.
For example, CacheAudit~\cite{182946} estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even those
tools report severe leakage, it does not mean the program has a truly severe leakage.
